---
title: "Supplemental Material"
editor: visual
---

```{r include=FALSE}
# packages
library(flextable)
library(dplyr)
library(stringr)
```

**Table 1.** *Claim phrases of the original authors in their discussion, where their hypothesis was supported*.

```{r include=FALSE}
# descriptives of supporting claims

# read lines
support_claim_lines <- readLines("data/nvivo_supporting_claims.txt", warn = FALSE)

# remove reference lines and coding notes
support_claim_lines <- support_claim_lines[!grepl("Reference", support_claim_lines)]
support_claim_lines <- support_claim_lines[!grepl("Files", support_claim_lines)]

# clean + lowercase
support_claim_clean <- support_claim_lines[support_claim_lines != ""]
support_claim_clean <- str_to_lower(str_squish(support_claim_clean))
support_claim_clean <- support_claim_clean[support_claim_clean != ""]

# frequency table 
support_claim_freq <- as.data.frame(table(support_claim_clean), stringsAsFactors = FALSE)
names(support_claim_freq) <- c("word", "freq")
support_claim_freq <- support_claim_freq %>% 
  arrange(desc(support_claim_freq$freq))

first_half_support_claim_freq <- support_claim_freq[1:29, ]
second_half_support_claim_freq <- support_claim_freq[30:58, ]

split_support_claim_freq <- cbind(first_half_support_claim_freq, second_half_support_claim_freq)
names(split_support_claim_freq) <- c("Term ", "Frequency ", "Term", "Frequency")

```

`r flextable(split_support_claim_freq) %>% fontsize(size = 6, part = "all") %>% padding(padding = 2, part = "all") %>% autofit()`

**Table 2.** *Claim phrases of the original authors in their discussion, where their hypothesis was not supported*.

```{r include = FALSE}
# descriptives of none supporting claims

# read lines
no_support_claim_lines <- readLines("data/nvivo_not_supporting_claims.txt", warn = FALSE)

# remove reference lines and coding notes
no_support_claim_lines <- no_support_claim_lines[!grepl("Reference", no_support_claim_lines)]
no_support_claim_lines <- no_support_claim_lines[!grepl("Files", no_support_claim_lines)]

# clean + lowercase
no_support_claim_clean <- no_support_claim_lines[no_support_claim_lines != ""]
no_support_claim_clean <- str_to_lower(str_squish(no_support_claim_clean))
no_support_claim_clean <- no_support_claim_clean[no_support_claim_clean != ""]

# frequency table 
no_support_claim_freq <- as.data.frame(table(no_support_claim_clean), stringsAsFactors = FALSE)
names(no_support_claim_freq) <- c("word", "freq")
no_support_claim_freq <- no_support_claim_freq %>% 
  arrange(desc(no_support_claim_freq$freq))

first_half_no_support_claim_freq <- no_support_claim_freq[1:15, ]
second_half_no_support_claim_freq <- no_support_claim_freq[16:30, ]

split_no_support_claim_freq <- cbind(first_half_no_support_claim_freq, second_half_no_support_claim_freq)
names(split_no_support_claim_freq) <- c("Term ", "Frequency ", "Term", "Frequency")

```

`r flextable(split_no_support_claim_freq) %>% fontsize(size = 6, part = "all") %>% padding(padding = 2, part = "all") %>% autofit()`

**Table 3.** *Claim phrases of the original authors in their discussion, where support for their hypothesis was "mixed"*.

```{r include = FALSE}
# descriptives of mixed claims

# read lines
mixed_claim_lines <- readLines("data/nvivo_mixed_claims.txt", warn = FALSE)

# remove reference lines and coding notes
mixed_claim_lines <- mixed_claim_lines[!grepl("Reference", mixed_claim_lines)]
mixed_claim_lines <- mixed_claim_lines[!grepl("Files", mixed_claim_lines)]

# clean + lowercase
mixed_claim_clean <- mixed_claim_lines[mixed_claim_lines != ""]
mixed_claim_clean <- str_to_lower(str_squish(mixed_claim_clean))
mixed_claim_clean <- mixed_claim_clean[mixed_claim_clean != ""]

# frequency table 
mixed_claim_freq <- as.data.frame(table(mixed_claim_clean), stringsAsFactors = FALSE)
names(mixed_claim_freq) <- c("word", "freq")
mixed_claim_freq <- mixed_claim_freq %>% 
  arrange(desc(mixed_claim_freq$freq))

first_half_mixed_claim_freq <- mixed_claim_freq[1:12, ]
second_half_mixed_claim_freq <- mixed_claim_freq[13:24, ]

split_mixed_claim_freq <- cbind(first_half_mixed_claim_freq, second_half_mixed_claim_freq)
names(split_mixed_claim_freq) <- c("Term ", "Frequency ", "Term", "Frequency")

```

`r flextable(split_mixed_claim_freq) %>% fontsize(size = 6, part = "all") %>% padding(padding = 2, part = "all") %>% autofit()`
